Mapping mutational effects along the evolutionary landscape of HIV envelope

### 2017-12-14 paper/manuscript.tex
added reference

But interpreting these studies in the context of Env evolution requires addressing a fundamental question: How informative are mutational studies of a single protein variant about constraints on long-term evolution?
During protein evolution, substitutions at one site can change the effect of mutations at other sites~\citep{natarajan2013epistasis,gong2013stability,harms2014historical,podgornaia2015pervasive,starr2016epistasis}.
We will follow the nomenclature of \citet{pollock2012amino} to refer to these changes in mutational effects as \emph{shifts} in a site's amino-acid preferences.
Such shifts can accumulate as substitutions become entrenched via epistatic interactions with subsequent changes~\citep{starr2017pervasive,pollock2012amino,shah2015contingency,bazykin2015changing} -- although the magnitude of these shifts is usually limited~\citep{doud2015site,chan2017correlation,ashenberg2013mutational,risso2014mutational}.
Given that the Envs of circulating HIV strains represent a vast collection of homologs that often differ at $>$100 residues, such shifts could make the outcome of any study highly dependent on the Env used.
The extent to which this is actually the case is unclear, since the few protein-wide studies of mutational shifts have examined proteins that are structurally far simpler than Env, which forms a large heavily glycosylated heterotrimeric complex that transitions through multiple conformational states~\citep{munro2014conformational,ozorowski2017open}.

>>>>

But interpreting these studies in the context of Env evolution requires addressing a fundamental question: How informative are mutational studies of a single protein variant about constraints on long-term evolution?
During protein evolution, substitutions at one site can change the effect of mutations at other sites~\citep{natarajan2013epistasis,gong2013stability,harms2014historical,podgornaia2015pervasive,starr2016epistasis,klink2017parallel}.
We will follow the nomenclature of \citet{pollock2012amino} to refer to these changes in mutational effects as \emph{shifts} in a site's amino-acid preferences.
Such shifts can accumulate as substitutions become entrenched via epistatic interactions with subsequent changes~\citep{starr2017pervasive,pollock2012amino,shah2015contingency,bazykin2015changing} -- although the magnitude of these shifts is usually limited~\citep{doud2015site,chan2017correlation,ashenberg2013mutational,risso2014mutational}.
Given that the Envs of circulating HIV strains represent a vast collection of homologs that often differ at $>$100 residues, such shifts could make the outcome of any study highly dependent on the Env used.
The extent to which this is actually the case is unclear, since the few protein-wide studies of mutational shifts have examined proteins that are structurally far simpler than Env, which forms a large heavily glycosylated heterotrimeric complex that transitions through multiple conformational states~\citep{munro2014conformational,ozorowski2017open}.
